
\begin{thebibliography}{99}

\addcontentsline{toc}{chapter}{\bibname}

\bibitem{1}
Onur Cinar, 2015, \emph{Android Quick APIs Reference}, Editura APRESS.

\bibitem{2}
Dave Smith, 2015, \emph{Android Recipes: A Problem-Solution Approach for Android 5.0},Editura APRESS.
\bibitem{3}
Wei-Meng Lee, 2012 \emph{BEGINNING Android 4 Application Development}, Editura Wrox Press

\bibitem{4}
Sayed Y. Hashimi and Satya Komatineni, 2009, \emph{Pro Android},
Editura APRESS.

\bibitem{5}
Open Handset Alliance, 2007, Industry Leaders Announce Open Platform for Mobile Devices. Press release., \newline\url{http://www.openhandsetalliance.com/press_110507.html}

\bibitem{6}
Google's Android parts ways with Java industry group,\url{ http://www.cnet.com/news/googles-android-parts-ways-with-java-industry-group/}

\bibitem{7}
General Android 2008,\newline\url{ http://code.google.com/android/kb/general.html}

\bibitem{8}
Native C application for Android, \newline\url{http://benno.id.au/blog/2007/11/13/android-native-apps}

\bibitem{9}
Android version history, \newline\url{http://en.wikipedia.org/wiki/Android_version_history#Pre-commercial_release_versions}

\bibitem{10}
http://www.oracle.com/technetwork/java/

\bibitem{11}
Barry Burd PhD, 2014, Beginning Programming with Java For Dummies, 4th Edition, Wiley eBooks

\bibitem{12}
Ştefan Tanasa, Cristian Olaru, Stefan Andrei, "Java de la 0 la expert", Polirom, 2003.

 \bibitem{13}
Yakov Fain, 2011, Java Programming 24-Hour Trainer, Wrox eBooks

 \bibitem{14}
Yvor Horton, 2011, Beginning Java , Java 7 Edition, John Wiley \& Sons, Inc.

\bibitem{15}
Adrian Deaconu, 2007, Programarea în C/C++ și aplicații , Grupul microInformatica, Cluj-Napoca

\bibitem{16}
Document Object Model (DOM). http://www.w3.org/: W3C., 2012

\bibitem{17}
Lawrence Rosen, OPEN SOURCE LICENSING, p.85 (Prentice Hall PTR, 1st ed. 2004)

\bibitem{18}
jsoup: Java HTML Parser, https://jsoup.org/

\bibitem{19}
Emanuele Delbono, 2013, ASP.NET Web API Succinctly, Syncfusion.

\bibitem{20}
Michael Collier, Robin Shahan, 2015, Fundamentals of Azure, Microsoft Press. Ed. APRESS.

\end{thebibliography}

